Legends for supplementary material

### 2019-05-14 Manuscript/Supplementary/supplementary_legends.Rmd
editted legends

**Supplementary Figure 1. GM12878 distance densities.** (A-D) Distances (in millions of basepairs) from the center of each genomic bin to the nearest annotation peak, for binwidths of 10 kb, 25 kb, 50 kb, and 100 kb. (E-H) $Log_{2}$ transformed distances for binwidths of 10 kb, 25 kb, 50 kb, and 100 kb.

**Supplementary Figure 2. K562 distance densities.** (A-D) Distances (in millions of basepairs) from the center of each genomic bin to the nearest annotation peak, for binwidths of 10 kb, 25 kb, 50 kb, and 100 kb. (E-H) $Log_{2}$ transformed distances for binwidths of 10 kb, 25 kb, 50 kb, and 100 kb.

>>>>

**Supplementary Figure 1. GM12878 distance densities.** (A-D) Distances (in millions of basepairs) from the center of each genomic bin to the nearest annotation peak, for binwidths (resolutions) of 10 kb, 25 kb, 50 kb, and 100 kb. (E-H) $Log_{2}$ transformed distances for binwidths (resolutions) of 10 kb, 25 kb, 50 kb, and 100 kb.

**Supplementary Figure 2. K562 distance densities.** (A-D) Distances (in millions of basepairs) from the center of each genomic bin to the nearest annotation peak, for binwidths (resolutions) of 10 kb, 25 kb, 50 kb, and 100 kb. (E-H) $Log_{2}$ transformed distances for binwidths (resolutions) of 10 kb, 25 kb, 50 kb, and 100 kb.
